---
title: "Logistic Regression Notebook"
author: "Jae Yong (Francisco) Lee"
output:
  pdf_document: default
  html_notebook: default
---

### Logistic Regression
```{r}
#install.packages("plyr")
#install.packages("corrplot")
#install.packages("gridExtra")
#install.packages("ggthemes")
#install.packages("caret")
#install.packages("MASS")
#install.packages("gplots")
library(gridExtra)
library(ggthemes)
library(caret)
library(MASS)
library(plyr)
library(corrplot)
library(ggplot2)
library(gplots)
```
Data Preparation

**Dealing with imbalanced class distribution**
Answers online: 
For logistic regression in particular, there was absolutely no benefit to creating a balanced sample. What was far more important was using all the data you had available. 

For logistic regression models unbalanced training data affects only the estimate of the model intercept (although this of course skews all the predicted probabilities, which in turn compromises your predictions). Fortunately the intercept correction is straightforward: Provided you know, or can guess, the true proportion of 0s and 1s and know the proportions in the training set you can apply a rare events correction to the intercept.

**How to remove outliers from dataset**
Unsolved

```{r}
#Import dataset
hoq <- read.csv(file="../dataset/final_hoq.csv", header = TRUE)
str(hoq)
```

Descriptive statistics for the attributes.
Check if there are any missing values in each attributes.
-There are no missing values for all attributes. 
```{r pressure, echo=FALSE}

summary(hoq)

sapply(hoq,function(x) sum(is.na(x)))
```

Correlation between categorical attributes. Checking if categorical variables are independent can be done with Chi-Squared test of independence.

If we assume that a given set of variables are independent, then the values of the contingency table for these variables should be distributed uniformly. After, we check how far away from uniform the actual values are.
-The Day Charge and Day minutes are correlated. So one of them will be removed from the model. We remove Day Charge. We also remove Eve Charge, Night Charge and Intl.Charge for the same reason.
```{r}
# Convert data as a table
dt <- as.table(as.matrix(hoq))
# Compute the frequency.
library(dplyr)
c(hoq$h_mortality,
  hoq$h_soc,
  hoq$h_ra,
  hoq$h_pex,
  hoq$h_eoc,
  hoq$h_toc,
  hoq$h_imaging)
df <- hoq$h_mortality %>%
  group_by(date) %>%
  summarise(counts = n())
df
# Graph
balloonplot(t(dt), main="Hospital Overall Ratings", xlab="", ylab="", label=FALSE, show.margins=FALSE)
```